### 2018-03-19 submission/manuscript.Rmd
add further discussion points

>>>>

- Add section on how this relates to the other components involved with 16S rRNA gene sequencing

- Add section on how this relates to previous PCR bias findings

- Bring everything back to the first paragraph that talks about bias, reproducibility and standardization

- End on a positive that these differences are probably masked by large biological variation and so have minimal impact on findings within a study (can be part of the previous bullet point).
